### 2020-06-21 compare_R0.tex
done

% Created by tikzDevice version 0.12.3 on 2020-05-07 17:27:07
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (578.16,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 27.31, 18.22) rectangle (572.66,247.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.31, 18.22) rectangle (572.66,247.13);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31, 25.76) --
	(572.66, 25.76);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31, 79.98) --
	(572.66, 79.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31,134.20) --
	(572.66,134.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31,188.41) --
	(572.66,188.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31,242.63) --
	(572.66,242.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31, 52.87) --
	(572.66, 52.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31,107.09) --
	(572.66,107.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31,161.31) --
	(572.66,161.31);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31,215.52) --
	(572.66,215.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.22, 18.22) --
	( 67.22,247.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (133.72, 18.22) --
	(133.72,247.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.23, 18.22) --
	(200.23,247.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (266.73, 18.22) --
	(266.73,247.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.24, 18.22) --
	(333.24,247.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (399.75, 18.22) --
	(399.75,247.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (466.25, 18.22) --
	(466.25,247.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.76, 18.22) --
	(532.76,247.13);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 55.23) -- (572.66, 55.23);

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,122.16) -- (572.66,122.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.65, 75.59) rectangle ( 70.79, 82.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.65, 75.59) -- ( 70.79, 82.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.65, 82.72) -- ( 70.79, 75.59);
\definecolor{drawColor}{RGB}{145,131,230}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.15, 78.87) -- (151.24, 78.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.19, 73.83) -- (146.19, 83.92);
\definecolor{fillColor}{RGB}{0,173,154}

\path[fill=fillColor] (134.31, 56.77) --
	(141.45, 56.77) --
	(141.45, 63.91) --
	(134.31, 63.91) --
	cycle;
\definecolor{fillColor}{RGB}{144,152,0}

\path[fill=fillColor] (129.57, 78.05) --
	(134.37, 69.73) --
	(124.76, 69.73) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (121.25, 66.37) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.65, 66.49) -- (217.74, 66.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.70, 61.44) -- (212.70, 71.54);
\definecolor{fillColor}{RGB}{0,173,154}

\path[fill=fillColor] (200.82, 65.00) --
	(207.95, 65.00) --
	(207.95, 72.13) --
	(200.82, 72.13) --
	cycle;
\definecolor{fillColor}{RGB}{144,152,0}

\path[fill=fillColor] (196.07, 84.79) --
	(200.88, 76.46) --
	(191.27, 76.46) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (187.76, 67.91) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.16, 66.66) -- (284.25, 66.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.20, 61.62) -- (279.20, 71.71);
\definecolor{fillColor}{RGB}{0,173,154}

\path[fill=fillColor] (267.32, 74.74) --
	(274.46, 74.74) --
	(274.46, 81.88) --
	(267.32, 81.88) --
	cycle;
\definecolor{fillColor}{RGB}{144,152,0}

\path[fill=fillColor] (262.58,100.58) --
	(267.38, 92.26) --
	(257.77, 92.26) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (254.26, 77.41) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.66,101.40) -- (350.76,101.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.71, 96.36) -- (345.71,106.45);
\definecolor{fillColor}{RGB}{0,173,154}

\path[fill=fillColor] (333.83,110.42) --
	(340.96,110.42) --
	(340.96,117.56) --
	(333.83,117.56) --
	cycle;
\definecolor{fillColor}{RGB}{144,152,0}

\path[fill=fillColor] (329.08, 78.47) --
	(333.89, 70.15) --
	(324.28, 70.15) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (320.77,101.64) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (407.17, 55.76) -- (417.26, 55.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.22, 50.72) -- (412.22, 60.81);
\definecolor{fillColor}{RGB}{0,173,154}

\path[fill=fillColor] (400.33, 46.35) --
	(407.47, 46.35) --
	(407.47, 53.48) --
	(400.33, 53.48) --
	cycle;
\definecolor{fillColor}{RGB}{144,152,0}

\path[fill=fillColor] (395.59,101.86) --
	(400.39, 93.54) --
	(390.78, 93.54) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (387.28, 56.59) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.67,105.92) -- (483.77,105.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.72,100.87) -- (478.72,110.97);
\definecolor{fillColor}{RGB}{0,173,154}

\path[fill=fillColor] (466.84,156.18) --
	(473.98,156.18) --
	(473.98,163.32) --
	(466.84,163.32) --
	cycle;
\definecolor{fillColor}{RGB}{144,152,0}

\path[fill=fillColor] (462.09, 95.96) --
	(466.90, 87.64) --
	(457.29, 87.64) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (453.78,145.76) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (540.18, 55.35) -- (550.27, 55.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (545.23, 50.30) -- (545.23, 60.40);
\definecolor{fillColor}{RGB}{0,173,154}

\path[fill=fillColor] (533.34, 66.58) --
	(540.48, 66.58) --
	(540.48, 73.72) --
	(533.34, 73.72) --
	cycle;
\definecolor{fillColor}{RGB}{144,152,0}

\path[fill=fillColor] (528.60,111.22) --
	(533.41,102.89) --
	(523.79,102.89) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (520.29, 66.12) circle (  3.57);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 67.22,122.16) --
	( 67.22,122.16);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 67.22,122.16) --
	( 67.22, 55.23);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 67.22, 55.23) --
	( 67.22, 55.23);
\definecolor{drawColor}{RGB}{145,131,230}

\path[draw=drawColor,line width= 1.1pt,line join=round] (146.19,148.57) --
	(146.19,148.57);

\path[draw=drawColor,line width= 1.1pt,line join=round] (146.19,148.57) --
	(146.19, 42.52);

\path[draw=drawColor,line width= 1.1pt,line join=round] (146.19, 42.52) --
	(146.19, 42.52);
\definecolor{drawColor}{RGB}{0,173,154}

\path[draw=drawColor,line width= 1.1pt,line join=round] (137.88, 83.60) --
	(137.88, 83.60);

\path[draw=drawColor,line width= 1.1pt,line join=round] (137.88, 83.60) --
	(137.88, 38.44);

\path[draw=drawColor,line width= 1.1pt,line join=round] (137.88, 38.44) --
	(137.88, 38.44);
\definecolor{drawColor}{RGB}{144,152,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (129.57, 93.55) --
	(129.57, 93.55);

\path[draw=drawColor,line width= 1.1pt,line join=round] (129.57, 93.55) --
	(129.57, 57.68);

\path[draw=drawColor,line width= 1.1pt,line join=round] (129.57, 57.68) --
	(129.57, 57.68);
\definecolor{drawColor}{RGB}{225,106,134}

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.25, 92.13) --
	(121.25, 92.13);

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.25, 92.13) --
	(121.25, 40.71);

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.25, 40.71) --
	(121.25, 40.71);
\definecolor{drawColor}{RGB}{145,131,230}

\path[draw=drawColor,line width= 1.1pt,line join=round] (212.70,109.43) --
	(212.70,109.43);

\path[draw=drawColor,line width= 1.1pt,line join=round] (212.70,109.43) --
	(212.70, 40.25);

\path[draw=drawColor,line width= 1.1pt,line join=round] (212.70, 40.25) --
	(212.70, 40.25);
\definecolor{drawColor}{RGB}{0,173,154}

\path[draw=drawColor,line width= 1.1pt,line join=round] (204.38,108.47) --
	(204.38,108.47);

\path[draw=drawColor,line width= 1.1pt,line join=round] (204.38,108.47) --
	(204.38, 40.60);

\path[draw=drawColor,line width= 1.1pt,line join=round] (204.38, 40.60) --
	(204.38, 40.60);
\definecolor{drawColor}{RGB}{144,152,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (196.07,112.61) --
	(196.07,112.61);

\path[draw=drawColor,line width= 1.1pt,line join=round] (196.07,112.61) --
	(196.07, 59.21);

\path[draw=drawColor,line width= 1.1pt,line join=round] (196.07, 59.21) --
	(196.07, 59.21);
\definecolor{drawColor}{RGB}{225,106,134}

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.76,105.16) --
	(187.76,105.16);

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.76,105.16) --
	(187.76, 40.54);

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.76, 40.54) --
	(187.76, 40.54);
\definecolor{drawColor}{RGB}{145,131,230}

\path[draw=drawColor,line width= 1.1pt,line join=round] (279.20, 84.95) --
	(279.20, 84.95);

\path[draw=drawColor,line width= 1.1pt,line join=round] (279.20, 84.95) --
	(279.20, 52.73);

\path[draw=drawColor,line width= 1.1pt,line join=round] (279.20, 52.73) --
	(279.20, 52.73);
\definecolor{drawColor}{RGB}{0,173,154}

\path[draw=drawColor,line width= 1.1pt,line join=round] (270.89,103.19) --
	(270.89,103.19);

\path[draw=drawColor,line width= 1.1pt,line join=round] (270.89,103.19) --
	(270.89, 59.79);

\path[draw=drawColor,line width= 1.1pt,line join=round] (270.89, 59.79) --
	(270.89, 59.79);
\definecolor{drawColor}{RGB}{144,152,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (262.58,154.24) --
	(262.58,154.24);

\path[draw=drawColor,line width= 1.1pt,line join=round] (262.58,154.24) --
	(262.58, 65.38);

\path[draw=drawColor,line width= 1.1pt,line join=round] (262.58, 65.38) --
	(262.58, 65.38);
\definecolor{drawColor}{RGB}{225,106,134}

\path[draw=drawColor,line width= 1.1pt,line join=round] (254.26, 97.96) --
	(254.26, 97.96);

\path[draw=drawColor,line width= 1.1pt,line join=round] (254.26, 97.96) --
	(254.26, 60.10);

\path[draw=drawColor,line width= 1.1pt,line join=round] (254.26, 60.10) --
	(254.26, 60.10);
\definecolor{drawColor}{RGB}{145,131,230}

\path[draw=drawColor,line width= 1.1pt,line join=round] (345.71,126.97) --
	(345.71,126.97);

\path[draw=drawColor,line width= 1.1pt,line join=round] (345.71,126.97) --
	(345.71, 74.24);

\path[draw=drawColor,line width= 1.1pt,line join=round] (345.71, 74.24) --
	(345.71, 74.24);
\definecolor{drawColor}{RGB}{0,173,154}

\path[draw=drawColor,line width= 1.1pt,line join=round] (337.40,131.59) --
	(337.40,131.59);

\path[draw=drawColor,line width= 1.1pt,line join=round] (337.40,131.59) --
	(337.40,100.29);

\path[draw=drawColor,line width= 1.1pt,line join=round] (337.40,100.29) --
	(337.40,100.29);
\definecolor{drawColor}{RGB}{144,152,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (329.08,101.76) --
	(329.08,101.76);

\path[draw=drawColor,line width= 1.1pt,line join=round] (329.08,101.76) --
	(329.08, 55.45);

\path[draw=drawColor,line width= 1.1pt,line join=round] (329.08, 55.45) --
	(329.08, 55.45);
\definecolor{drawColor}{RGB}{225,106,134}

\path[draw=drawColor,line width= 1.1pt,line join=round] (320.77,107.13) --
	(320.77,107.13);

\path[draw=drawColor,line width= 1.1pt,line join=round] (320.77,107.13) --
	(320.77, 96.34);

\path[draw=drawColor,line width= 1.1pt,line join=round] (320.77, 96.34) --
	(320.77, 96.34);
\definecolor{drawColor}{RGB}{145,131,230}

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.22, 98.29) --
	(412.22, 98.29);

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.22, 98.29) --
	(412.22, 29.35);

\path[draw=drawColor,line width= 1.1pt,line join=round] (412.22, 29.35) --
	(412.22, 29.35);
\definecolor{drawColor}{RGB}{0,173,154}

\path[draw=drawColor,line width= 1.1pt,line join=round] (403.90, 91.28) --
	(403.90, 91.28);

\path[draw=drawColor,line width= 1.1pt,line join=round] (403.90, 91.28) --
	(403.90, 28.63);

\path[draw=drawColor,line width= 1.1pt,line join=round] (403.90, 28.63) --
	(403.90, 28.63);
\definecolor{drawColor}{RGB}{144,152,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (395.59,165.53) --
	(395.59,165.53);

\path[draw=drawColor,line width= 1.1pt,line join=round] (395.59,165.53) --
	(395.59, 61.03);

\path[draw=drawColor,line width= 1.1pt,line join=round] (395.59, 61.03) --
	(395.59, 61.03);
\definecolor{drawColor}{RGB}{225,106,134}

\path[draw=drawColor,line width= 1.1pt,line join=round] (387.28, 96.20) --
	(387.28, 96.20);

\path[draw=drawColor,line width= 1.1pt,line join=round] (387.28, 96.20) --
	(387.28, 29.36);

\path[draw=drawColor,line width= 1.1pt,line join=round] (387.28, 29.36) --
	(387.28, 29.36);
\definecolor{drawColor}{RGB}{145,131,230}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-06-20 18:53:21
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (578.16,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 27.31, 18.22) rectangle (572.66,232.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 27.31, 18.22) rectangle (572.66,232.67);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31, 25.29) --
	(572.66, 25.29);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31, 76.08) --
	(572.66, 76.08);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31,126.87) --
	(572.66,126.87);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31,177.67) --
	(572.66,177.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 27.31,228.46) --
	(572.66,228.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31, 50.68) --
	(572.66, 50.68);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31,101.48) --
	(572.66,101.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31,152.27) --
	(572.66,152.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.31,203.06) --
	(572.66,203.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.22, 18.22) --
	( 67.22,232.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (133.72, 18.22) --
	(133.72,232.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (200.23, 18.22) --
	(200.23,232.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (266.73, 18.22) --
	(266.73,232.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (333.24, 18.22) --
	(333.24,232.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (399.75, 18.22) --
	(399.75,232.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (466.25, 18.22) --
	(466.25,232.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.76, 18.22) --
	(532.76,232.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31, 52.89) -- (572.66, 52.89);

\path[draw=drawColor,draw opacity=0.50,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,115.60) -- (572.66,115.60);
\definecolor{drawColor}{RGB}{182,117,224}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.65, 71.74) -- ( 70.79, 78.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.65, 78.88) -- ( 70.79, 71.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.17, 75.31) -- ( 72.26, 75.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.22, 70.26) -- ( 67.22, 80.35);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.45, 71.47) rectangle (150.59, 78.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.45, 71.47) -- (150.59, 78.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.45, 78.61) -- (150.59, 71.47);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.33, 57.68) -- (145.42, 57.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.37, 52.63) -- (140.37, 62.73);
\definecolor{fillColor}{RGB}{170,144,0}

\path[fill=fillColor] (130.15, 65.51) --
	(137.29, 65.51) --
	(137.29, 72.64) --
	(130.15, 72.64) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (127.07, 68.88) --
	(131.88, 60.55) --
	(122.27, 60.55) --
	cycle;
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.96, 59.87) rectangle (217.10, 67.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.96, 59.87) -- (217.10, 67.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.96, 67.01) -- (217.10, 59.87);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.83, 65.39) -- (211.93, 65.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.88, 60.34) -- (206.88, 70.43);
\definecolor{fillColor}{RGB}{170,144,0}

\path[fill=fillColor] (196.66, 71.82) --
	(203.80, 71.82) --
	(203.80, 78.95) --
	(196.66, 78.95) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (193.58, 70.32) --
	(198.38, 62.00) --
	(188.77, 62.00) --
	cycle;
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (186.93, 65.92) circle (  3.57);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.47, 60.04) rectangle (283.60, 67.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.47, 60.04) -- (283.60, 67.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.47, 67.17) -- (283.60, 60.04);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.34, 74.52) -- (278.43, 74.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.38, 69.47) -- (273.38, 79.56);
\definecolor{fillColor}{RGB}{170,144,0}

\path[fill=fillColor] (263.17, 86.61) --
	(270.30, 86.61) --
	(270.30, 93.75) --
	(263.17, 93.75) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (260.08, 79.22) --
	(264.89, 70.90) --
	(255.28, 70.90) --
	cycle;
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (253.43, 74.05) circle (  3.57);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.97, 92.58) rectangle (350.11, 99.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.97, 92.58) -- (350.11, 99.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.97, 99.72) -- (350.11, 92.58);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.84,107.95) -- (344.94,107.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (339.89,102.90) -- (339.89,112.99);
\definecolor{fillColor}{RGB}{170,144,0}

\path[fill=fillColor] (329.67, 65.90) --
	(336.81, 65.90) --
	(336.81, 73.04) --
	(329.67, 73.04) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (326.59,101.92) --
	(331.40, 93.60) --
	(321.78, 93.60) --
	cycle;
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (319.94, 96.40) circle (  3.57);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.48, 49.82) rectangle (416.61, 56.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.48, 49.82) -- (416.61, 56.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.48, 56.96) -- (416.61, 49.82);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.35, 47.91) -- (411.44, 47.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.40, 42.87) -- (406.40, 52.96);
\definecolor{fillColor}{RGB}{170,144,0}

\path[fill=fillColor] (396.18, 87.82) --
	(403.31, 87.82) --
	(403.31, 94.95) --
	(396.18, 94.95) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (393.09, 59.72) --
	(397.90, 51.39) --
	(388.29, 51.39) --
	cycle;
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (386.44, 55.76) circle (  3.57);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.98, 96.81) rectangle (483.12,103.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.98, 96.81) -- (483.12,103.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.98,103.95) -- (483.12, 96.81);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.85,150.81) -- (477.95,150.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.90,145.76) -- (472.90,155.86);
\definecolor{fillColor}{RGB}{170,144,0}

\path[fill=fillColor] (462.68, 82.29) --
	(469.82, 82.29) --
	(469.82, 89.42) --
	(462.68, 89.42) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (459.60,143.26) --
	(464.41,134.93) --
	(454.79,134.93) --
	cycle;
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (452.95,138.81) circle (  3.57);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (542.49, 49.44) rectangle (549.63, 56.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (542.49, 49.44) -- (549.63, 56.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (542.49, 56.57) -- (549.63, 49.44);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.36, 66.87) -- (544.45, 66.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (539.41, 61.82) -- (539.41, 71.92);
\definecolor{fillColor}{RGB}{170,144,0}

\path[fill=fillColor] (529.19, 96.58) --
	(536.33, 96.58) --
	(536.33,103.71) --
	(529.19,103.71) --
	cycle;
\definecolor{fillColor}{RGB}{225,106,134}

\path[fill=fillColor] (526.11, 68.64) --
	(530.91, 60.32) --
	(521.30, 60.32) --
	cycle;
\definecolor{drawColor}{RGB}{182,117,224}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 67.22,115.60) --
	( 67.22,115.60);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 67.22,115.60) --
	( 67.22, 52.89);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 67.22, 52.89) --
	( 67.22, 52.89);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 1.1pt,line join=round] (147.02,140.34) --
	(147.02,140.34);

\path[draw=drawColor,line width= 1.1pt,line join=round] (147.02,140.34) --
	(147.02, 40.98);

\path[draw=drawColor,line width= 1.1pt,line join=round] (147.02, 40.98) --
	(147.02, 40.98);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 1.1pt,line join=round] (140.37, 79.47) --
	(140.37, 79.47);

\path[draw=drawColor,line width= 1.1pt,line join=round] (140.37, 79.47) --
	(140.37, 37.16);

\path[draw=drawColor,line width= 1.1pt,line join=round] (140.37, 37.16) --
	(140.37, 37.16);
\definecolor{drawColor}{RGB}{170,144,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (133.72, 88.80) --
	(133.72, 88.80);

\path[draw=drawColor,line width= 1.1pt,line join=round] (133.72, 88.80) --
	(133.72, 55.19);

\path[draw=drawColor,line width= 1.1pt,line join=round] (133.72, 55.19) --
	(133.72, 55.19);
\definecolor{drawColor}{RGB}{225,106,134}

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.07, 87.46) --
	(127.07, 87.46);

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.07, 87.46) --
	(127.07, 39.29);

\path[draw=drawColor,line width= 1.1pt,line join=round] (127.07, 39.29) --
	(127.07, 39.29);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.42, 88.78) --
	(120.42, 88.78);

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.42, 88.78) --
	(120.42, 37.98);

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.42, 37.98) --
	(120.42, 37.98);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.53,103.67) --
	(213.53,103.67);

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.53,103.67) --
	(213.53, 38.86);

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.53, 38.86) --
	(213.53, 38.86);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 1.1pt,line join=round] (206.88,102.77) --
	(206.88,102.77);

\path[draw=drawColor,line width= 1.1pt,line join=round] (206.88,102.77) --
	(206.88, 39.19);

\path[draw=drawColor,line width= 1.1pt,line join=round] (206.88, 39.19) --
	(206.88, 39.19);
\definecolor{drawColor}{RGB}{170,144,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (200.23,106.65) --
	(200.23,106.65);

\path[draw=drawColor,line width= 1.1pt,line join=round] (200.23,106.65) --
	(200.23, 56.62);

\path[draw=drawColor,line width= 1.1pt,line join=round] (200.23, 56.62) --
	(200.23, 56.62);
\definecolor{drawColor}{RGB}{225,106,134}

\path[draw=drawColor,line width= 1.1pt,line join=round] (193.58, 99.67) --
	(193.58, 99.67);

\path[draw=drawColor,line width= 1.1pt,line join=round] (193.58, 99.67) --
	(193.58, 39.13);

\path[draw=drawColor,line width= 1.1pt,line join=round] (193.58, 39.13) --
	(193.58, 39.13);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] (186.93, 88.78) --
	(186.93, 88.78);

\path[draw=drawColor,line width= 1.1pt,line join=round] (186.93, 88.78) --
	(186.93, 37.98);

\path[draw=drawColor,line width= 1.1pt,line join=round] (186.93, 37.98) --
	(186.93, 37.98);
\definecolor{drawColor}{RGB}{0,166,202}

\path[draw=drawColor,line width= 1.1pt,line join=round] (280.03, 80.74) --
	(280.03, 80.74);

\path[draw=drawColor,line width= 1.1pt,line join=round] (280.03, 80.74) --
	(280.03, 50.55);

\path[draw=drawColor,line width= 1.1pt,line join=round] (280.03, 50.55) --
	(280.03, 50.55);
\definecolor{drawColor}{RGB}{0,170,90}

\path[draw=drawColor,line width= 1.1pt,line join=round] (273.38, 97.82) --
	(273.38, 97.82);

\path[draw=drawColor,line width= 1.1pt,line join=round] (273.38, 97.82) --
	(273.38, 57.16);

\path[draw=drawColor,line width= 1.1pt,line join=round] (273.38, 57.16) --
	(273.38, 57.16);
\definecolor{drawColor}{RGB}{170,144,0}
